A non-contextual hidden variable model for quantum mechanics

### 2017-02-08 finalPaper.tex
- ‘.#finalPaper.tex’ / ‘finalPaper.tex’
/ ‘finalPaper.tex’

consistent with all {\color{red} kinematic
predictions of} quantum

@@

contextuality is not a necessary feature of QM.

@@

consistent with QM  while remaining

@@

with QM~\cite{BellOnHiddenVariables}, and we in
this letter present a new non-contextual HV model

>>>>

consistent with all \color{red} kinematic
predictions of quantum

@@

contextuality is not a necessary feature of Quantum Statics (QS).

@@

consistent with QS  while remaining

@@

with QM~\cite{BellOnHiddenVariables}, and we, in
this letter, present a new non-contextual HV model
